MSDS6306_CaseStudy_2

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Updates to rmd
Keep_md TRUE

---
title: "MSDS6306_CaseStudy_2"
author: "Megan Hodges and Vivek Viswanathan"
date: "December 4, 2017"
output: html_document
---

@@

#### The data file has been read and stored in a temporary data frame (ProcrastinationData). The column names have been standardized to be 12 characters long or lesser.

>>>>

---
title: "MSDS6306_CaseStudy_2"
author: "Megan Hodges and Vivek Viswanathan"
date: "December 4, 2017"
output: 
  html_document:
    keep_md: true
---

@@

#### The data file has been read and stored in a temporary data frame (ProcrastinationData). The column names have been standardized to be 12 characters long or lesser.
#### The Column name mapping between the source csv file and the data frame can be found at the below path:
#### https://github.com/vviswanathan/MSDS6306_CaseStudy_2/blob/master/Presentation/Procrastination_Column_Name_Mapping.csv
